Pillar 1 - Student Topic Profile

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
join student topic profile to cumulative transcript
So that we can regression grade on topic profile

```{r}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")

@@

  mutate_at(vars(matches("Topic")), lag) %>% # topic profile of student at time t
  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>% # topic profile of student at time t
  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t

  right_join(d_transcript_informative, by = c("Student ID", "time")) %>%

  select(`Student ID`, `Course ID`, time, everything()) %>%
  arrange(`Student ID`)
```

>>>>

```{r}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/d_transcript_cum.RDATA")

@@

  mutate_at(vars(matches("Topic")), lag) %>%
  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>%
  mutate_at(vars(matches("Topic")), cumsum) # topic profile at beginning of period
```

```{r}
d_transcript_cum %>%

  right_join(student_TP, by = c("sequenceID" = "Student ID", "eventID" = "time"))
```
